Associations of environmental and human factors with altered rodent populations in West Africa: A scoping review

### 2021-04-28 reports/manuscript.Rmd
add toc

---
title: "Associations of environmental and human factors with altered rodent populations in West Africa: A scoping review"
description: |
date: "`r Sys.Date()`"
author: 
  - first_name: "David"
    last_name: "Simons"
    url: https://www.dsimons.org
    orcid_id: 0000-0001-9655-1656
output: 
  distill::distill_article:
  toc: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: "`r here::here('citations', 'manuscript_citations.bib')`"
---

>>>>

---
title: "Associations of environmental and human factors with altered rodent populations in West Africa: A scoping review"
description: |
date: "`r Sys.Date()`"
author: 
  - first_name: "David"
    last_name: "Simons"
    url: https://www.dsimons.org
    orcid_id: 0000-0001-9655-1656
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: "`r here::here('citations', 'manuscript_citations.bib')`"
---
